Modelling RNA-based oscillatory circuits

### 2015-09-28 Presentation/MscPresentation.tex
more presentation work

% Structuring a talk is a difficult task and the following structure
% may not be suitable. Here are some rules that apply for this
% solution:

% - Exactly two or three sections (other than the summary).
% - At *most* three subsections per section.
% - Talk about 30s to 2min per frame. So there should be between about
%   15 and 30 frames, all told.

% - A conference audience is likely to know very little of what you
%   are going to talk about. So *simplify*!
% - In a 20min talk, getting the main ideas across is hard
%   enough. Leave out details, even if it means being less precise than
%   you think necessary.
% - If you omit details that are vital to the proof/implementation,
%   just say so once. Everybody will be happy with that.

@@

\begin{frame}{The RNA System}{}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.
  \begin{center}
  \includegraphics[trim = 0 0 0 30,clip = true,scale = 0.275]{Figures/schematic_initial.png}
  \end{center}

  \begin{itemize}
    \item  mRNA produced `self repressed'  - tail folded over the RBS
    \item  sRNA binds to it - new complex has RBS uncovered.
    \end{itemize}
\end{frame}

\subsection{ODE Model for system}
\begin{frame}{ODE Model for system (1) - Complex Formation}{}
\begin{columns}
\column{.4\textwidth}
\includegraphics[trim = 135 0 0 0,clip = true,scale = 0.28]{Figures/schematic_binding}
\column{.6\textwidth}
  \begin{itemize}
    \item  Hybridization of sRNA \textcolor{blue}{($s$)} and mRNA \textcolor{blue}{($m$)}, into unstable complex \textcolor{blue}{($s:m$)} then stable one \textcolor{blue}{($c$)}.
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{d\textcolor{blue}{s}}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{d\textcolor{blue}{m}}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{d\textcolor{blue}{s:m}}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{d\textcolor{blue}{c}}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  \\
\end{align*}
\end{columns}
\end{frame}

\begin{frame}{ODE Model for system (2) - Translation}{}
\begin{columns}
\column{.4\textwidth}
\includegraphics[trim = 0 0 0 0,clip = true,scale = 0.31]{Figures/schematic_translation}
\column{.6\textwidth}
  \begin{itemize}
    \item Translation of stable complex \textcolor{blue}{($c$)} into immature GFP \textcolor{blue}{($p$)}. 
    \item maturation of GFP \textcolor{blue}{($g$)}, machine calibration giving measured fluorescence ($z$).
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{d\textcolor{blue}{p}}{dt} & = \beta m +f_{s}\beta c -(\gamma + \mu + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{d\textcolor{blue}{g}}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\Theta} 
\end{align*}
\end{columns}
\end{frame}

@@

\small
\begin{frame}{Full model, with Parameters to be estimated}
\begin{align} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align}
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\end{frame}
\normalsize

@@

\begin{frame}{Method for Parameter Estimation in ODE Model}
  \begin{block}{Goal}
 Estimate unknown parameters in model using time series data.
    \end{block}

      \begin{itemize}
    \item  Least squares error minimization approach
    \begin{align*}
\argmin_{\boldsymbol{\theta}} \sum_{i =1}^{n} (z_{\mathrm{exp, mean}}(t_{i}) - z(t_{i},\boldsymbol{\theta}))^2.
\end{align*}
\item Used evolutionary algorithm, CMA-ES, to perform minimisation.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.28, clip = true, trim = 80 0 0 0]{Figures/13_9_bestPlot}
\end{frame}

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.28, clip = true, trim = 130 0 0 0]{Figures/13_9_hist}
        \begin{itemize}
    \item Many parameters poorly estimated.
            \end{itemize}
\end{frame}

\begin{frame}{Sensitivity Analysis}
  \includegraphics[scale = 0.25, clip = true, trim = 00 0 0 0]{Figures/Sensitivty_scaled_other}
  \vspace{-2mm}
          \begin{itemize}
    \item Sensitivity analysis suggests perturbations of several parameters all give similar effects on model output - \alert{hard to resolve}
            \end{itemize}
\end{frame}

\begin{frame}{Model output for all state variables}
  \includegraphics[scale = 0.29, clip = true, trim = 0 0 0 0]{Figures/model_output}
\end{frame}

\small
\begin{frame}{Full model again}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align*}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*} 
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align*}
\end{frame}
\normalsize

\small
\begin{frame}{Simplified Model}
\begin{greyedout}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{ds:m}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{dc}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  
\end{align*}
\end{greyedout}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*} 
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}}  
\end{align*}
\end{frame}
\normalsize

\begin{frame}{Simplified Model}
\begin{align}
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\begin{itemize}
\item  Model only rate limiting steps - force translation term directly.
\item 3 unknown parameters
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (1)}
  \includegraphics[scale = 0.29, clip = true, trim = 100 0 0 400]{Figures/13_9_hist_simplified}
  \begin{itemize}
\item  Error values as low as full model
\item Clearer parameter estimation results
\item Two peak structure due to local minima
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (2)}
  \includegraphics[scale = 0.26, clip = true, trim = 40 0 0 0]{Figures/Likelihood_rough_presentation}
    \begin{itemize}
\item  Error landscape, $\Theta = 5400$.
\end{itemize}
\end{frame}

@@

\begin{frame}{Future Work}

  % Keep the summary *very short*.
  \begin{itemize}
  \item Fluorescence data \alert {not enough} to estimate all unknown parameters 
  \begin{itemize}
  \item Further experiments ?
  \item Bounds on unknown parameter values.
  \end{itemize} 
  \item Improve modelling of translation step
  \item Change methodology - Bayesian Methods?

  \end{itemize}

  \end{frame}

  \section*{Summary}

>>>>

\begin{frame}{Objectives}{}
  \begin{itemize}
    \item  Rational design of genetic circuits now possible
      \begin{itemize}
      \item ODE models used for prediction.
      \item Model parameters unknown.
      \end{itemize}
    \item Project studied a recently designed genetic circuit, attempted parameter estimation.
    \item Parameter estimates would inform future design/experiments.
        \end{itemize}
\end{frame}

@@

\begin{frame}{The RNA System}{}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.
  \begin{center}
  \includegraphics[trim = 370 0 0 200,clip = true,scale = 0.4]{Figures/schematic_initial_with_forcing.png}
  \end{center}

  \begin{itemize}
    \item  mRNA produced `self repressed'  - tail folded over the RBS
    \item  sRNA binds to it - new complex has RBS uncovered.
    \item Complex translated into proteins.
    \end{itemize}
\end{frame}

\subsection{ODE Model for system}
\begin{frame}{ODE model for system (1) - Binding step}{}
\begin{columns}
\column{.4\textwidth}
\includegraphics[trim = 135 0 0 0,clip = true,scale = 0.28]{Figures/schematic_binding}
\column{.6\textwidth}
  \begin{itemize}
    \item  Binding of sRNA \textcolor{blue}{($s$)} and mRNA \textcolor{blue}{($m$)}, into unstable complex \textcolor{blue}{($s:m$)} then stable one \textcolor{blue}{($c$)}.
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{d\textcolor{blue}{s}}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{d\textcolor{blue}{m}}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{d\textcolor{blue}{s:m}}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{d\textcolor{blue}{c}}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  \\
\end{align*}
\end{columns}
\end{frame}

\begin{frame}{ODE model for system (2) - Translation step}
\begin{columns}
\column{.4\textwidth}
\includegraphics[trim = 0 0 0 0,clip = true,scale = 0.31]{Figures/schematic_translation}
\column{.6\textwidth}
  \begin{itemize}
    \item Translation of stable complex \textcolor{blue}{($c$)} into immature GFP \textcolor{blue}{($p$)}. 
    \item maturation of GFP \textcolor{blue}{($g$)}, machine calibration giving measured fluorescence ($z$).
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{d\textcolor{blue}{p}}{dt} & = \beta m +f_{s}\beta c -(\gamma + \mu + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{d\textcolor{blue}{g}}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\Theta} 
\end{align*}
\end{columns}
\end{frame}

@@

\small
\begin{frame}{Full model, with parameters to be estimated}
\begin{align} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align}
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\end{frame}
\normalsize

\begin{frame}{Recent experimental data}{}
   \includegraphics[trim = 0 300 0 300,clip = true,scale = 0.55]{Figures/13_9}
  \begin{itemize}
    \item Single cell fluoresence time series data (Jaramillo Lab, unpublished).
    \item  Data records $z= z_{0} +\frac{g}{\alert{\Theta}} $
    \end{itemize}
\end{frame}

@@

\begin{frame}{Method for parameter estimation in ODE model}
  \begin{block}{Goal}
 Estimate unknown parameters in model using time series data.
    \end{block}

      \begin{itemize}
    \item  Least squares error minimization approach
    \begin{align*}
\argmin_{\boldsymbol{\theta}} \sum_{i =1}^{n} (z_{\mathrm{exp, mean}}(t_{i}) - z(t_{i},\boldsymbol{\theta}))^2.
\end{align*}
\item Used evolutionary algorithm to perform minimisation.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Initial estimation results}
  \includegraphics[scale = 0.28, clip = true, trim = 80 0 0 0]{Figures/13_9_bestPlot}
\end{frame}

\begin{frame}{Initial estimation results}
  \includegraphics[scale = 0.27, clip = true, trim = 130 0 0 50]{Figures/13_9_hist}
  \vspace{-10mm}
        \begin{itemize}
    \item Similar error values for all results.
    \item Many parameters poorly estimated.
            \end{itemize}
\end{frame}

\begin{frame}{Sensitivity analysis}
\begin{columns}
\column{.4\textwidth}
 \LARGE
\begin{align*}
S_{ij} =  \frac{\partial z}{ \partial \theta_{j}}\Bigr|_{t_{i}}
\end{align*}
\normalsize
\column{.59\textwidth}
Perturbations of parameters all give similar effects on model output - \alert{hard to distinguish}
\end{columns}
  \includegraphics[scale = 0.25, clip = true, trim = 00 0 0 0]{Figures/Sensitivty_scaled_other}
\end{frame}

\small
\begin{frame}{Full model, with parameters to be estimated}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align*}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*}
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align*}
\end{frame}
\normalsize

\begin{frame}{Model output for all state variables}
  \includegraphics[scale = 0.26, clip = true, trim = 0 0 0 0]{Figures/model_output}
  \begin{itemize}
    \item $s,m,s:m,c$ \alert{(binding step)} respond instantly to forcing.
    \item $p, z$ \alert{(translation step)} on timescale of forcing.
\end{itemize}
\end{frame}

\footnotesize
\begin{frame}{Translation rate limiting}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align*}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*} 
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align*}
\normalsize
\vspace{-5mm}
  \begin{itemize}
  \item Binding equations respond instantly.
    \item $ \alert{\beta} m +\alert{f_{s}}\beta c $ term links binding and translation. It flips between fixed point values.
    \item All parameters `upstream' have identical effects.
\end{itemize}
\end{frame}

\small
\begin{frame}{Simplified model}
\begin{greyedout}
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{ds:m}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{dc}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  
\end{align*}
\end{greyedout}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align*} 
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}}  
\end{align*}
\end{frame}
\normalsize

\begin{frame}{Simplified model}
\begin{align}
\frac{dp}{dt} & = \alert{F}y(t)-(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g}  \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\begin{itemize}
\item  Model only rate limiting steps - force translation term directly.
\item 3 unknown parameters
\end{itemize}
\end{frame}

\begin{frame}{Simplified model results (1)}
  \includegraphics[scale = 0.29, clip = true, trim = 100 0 0 400]{Figures/13_9_hist_simplified}
  \begin{itemize}
\item  Error values as low as full model
\item Clearer parameter estimation results
\item Two peak structure due to local minima
\end{itemize}
\end{frame}

\begin{frame}{Simplified model results (2)}
  \includegraphics[scale = 0.26, clip = true, trim = 40 0 0 0]{Figures/Likelihood_rough_presentation}
    \begin{itemize}
\item  Error landscape, $\Theta = 5400$.
\end{itemize}
\end{frame}

@@

\begin{frame}{Future work}
  \begin{itemize}
  \item Fluorescence data \alert {not enough} to estimate all unknown parameters 
  \item Further experiments needed - observe fast timescale.
  \item Investigate methods of McAuley et al. 
  \item Change methodology - Bayesian Methods?
  \end{itemize}
  \end{frame}

  \begin{frame}{Acknowledgements}
  \begin{itemize}
  \item Manish Kushawaha, Jaramillo Lab - School of Life Sciences
  \item Shenshi Shen, Boris Kisov for data.
  \item Annabelle Ballesta - Systems Biology
  \end{itemize}
  \end{frame}
